---
title: "George New Project"
output: html_notebook
---

```{r}
library(RPostgres)
wrds <- dbConnect(Postgres(),
                  host='wrds-pgdata.wharton.upenn.edu',
                  port=9737,
                  dbname='wrds',
                  sslmode='require',
                  user='echoi98')
library(tidyverse)
library(dbplyr)
```
Pull in the companies from crsp to IBES link 
```{r}
link_tool_v1<-read.csv("crsp_ibes_link.csv",header = TRUE)
link_tool_v1<- link_tool_v1%>%filter(SCORE!=6)
link_tool_ticker <- subset(link_tool_v1, select = c('TICKER','NCUSIP','PERMNO'))
```
Compu stat pull
```{r}
res <- dbSendQuery(wrds, "select gvkey, datadate, conm,cusip, fyr, fyear, exchg, bkvlps, epsfx, fic from comp.funda
                   where
                   fyr = '12' and 
                   exchg <> 0 and 
                   exchg <> 1 and
                   exchg <> 19 and
                   popsrc = 'D' and 
                   consol = 'C' and 
                   datafmt = 'STD'")
compustat_data <- dbFetch(res, n=-1)
dbClearResult(res)
head(compustat_data)
```
# Clean Compustat Data
```{r}
compustat_data_v1<-compustat_data
compustat_data_v1<- compustat_data_v1%>%drop_na(bkvlps)
```
# Grab the Security files for compustat for us first
```{r}
res <- dbSendQuery(wrds, "select gvkey, ibtic from comp.security")
compustat_security_data <- dbFetch(res, n=-1)
dbClearResult(res)
```
# Take out any NA's in compustat security
```{r}
compustat_security_data_v1<-compustat_security_data
compustat_security_data_v1<- compustat_security_data_v1%>%drop_na(ibtic)
head(compustat_security_data_v1)
```
# Grab the Security files for compustat for global first
```{r}
res <- dbSendQuery(wrds, "select gvkey, ibtic from comp.g_security")
compustat_global_security_data <- dbFetch(res, n=-1)
dbClearResult(res)
```
# Take out any NA's in  global compustat security
```{r}
compustat_global_security_data_v1<-compustat_global_security_data
compustat_global_security_data_v1<- compustat_global_security_data_v1%>%drop_na(ibtic)
head(compustat_global_security_data_v1)
```
# Merge both global and NA compustat to ibes link
```{r}
compustat_link_to_IBES<-rbind(compustat_security_data_v1, compustat_global_security_data_v1)
head(compustat_link_to_IBES)
```
# Now merge this with the original compustat data to have the link to IBES
```{r}
compustat_data_v2<- inner_join(compustat_data_v1, compustat_link_to_IBES, by =c('gvkey'='gvkey'))
compustat_data_v2<-compustat_data_v2%>%group_by(gvkey)
compustat_data_v2
```
# Now only include companies that are tracked by both IBES and CRSP using the link tool
```{r}
compustat_data_v3 <- inner_join(compustat_data_v2, link_tool_ticker, by = c('ibtic'='TICKER'))
compustat_data_v3
```
# Save this data to an excel 
```{r}
write.csv(compustat_data_v3,"compustat_data_vf.csv")
```
##################################################################################################################################################################################################################################
IBES pull
##################################################################################################################################################################################################################################
Pull International IBES Summary Data
```{r}
res <- dbSendQuery(wrds, "select ticker, cusip,cname,fiscalp,statpers,actual, anndats_act, actdats_act,numest,meanest, medest,fpedats,usfirm, fpi from ibes.NSTATSUM_EPSINT
                   where fiscalp = 'ANN' 
                   ")
ibes_int_stat_sum_data <- dbFetch(res, n=-1)
dbClearResult(res)
head(ibes_int_stat_sum_data)
```
Pull US IBES Summary Data
```{r}
res <- dbSendQuery(wrds, "select ticker, cusip,cname,fiscalp,statpers,actual, anndats_act, actdats_act,numest,meanest, medest,fpedats,usfirm,fpi from ibes.NSTATSUM_EPSUs
                   where fiscalp = 'ANN' and 
                   numest >=1
                   ")
ibes_US_stat_sum_data <- dbFetch(res, n=-1)
dbClearResult(res)
head(ibes_US_stat_sum_data)
```
Merger both ibes together
```{r}
complete_ibes_data<-rbind(ibes_int_stat_sum_data, ibes_US_stat_sum_data)
head(complete_ibes_data)
```
Rename the columns 
```{r}
complete_ibes_data_v1<-complete_ibes_data
complete_ibes_data_v1<-rename(complete_ibes_data_v1,forecast_date=statpers, actual_earnings=actual, forecasted_period=fpedats)
complete_ibes_data_v1<-complete_ibes_data_v1%>%group_by(ticker)
complete_ibes_data_v1
```
Only get fiscal year 12 end, forecast period of 1 (FPI) and take out nas 
```{r}
complete_ibes_data_v2<-complete_ibes_data_v1
# Month where the analyst forecasted
complete_ibes_data_v2$fiscal_year_end_month <- format(complete_ibes_data_v2$forecasted_period,"%m")
complete_ibes_data_v2<-complete_ibes_data_v2%>%filter(fiscal_year_end_month==12)
complete_ibes_data_v2<-complete_ibes_data_v2%>% filter(fpi==1)
complete_ibes_data_v2<-complete_ibes_data_v2%>% drop_na(actual_earnings)
```
Find the largest forecast date for any given forecast year 
```{r}
largest_forecast_date_max <- complete_ibes_data_v2%>%group_by(ticker,forecasted_period)%>%summarise(max=max(forecast_date))
largest_forecast_date_min <- complete_ibes_data_v2%>%group_by(ticker,forecasted_period)%>%summarise(min=min(forecast_date))
largest_forecast_date_max
largest_forecast_date_min
```
Create IBES consensus forecast database
```{r}
ibes_forecast_first_forecast<-inner_join(complete_ibes_data_v2,largest_forecast_date_min,by=c('ticker'='ticker','forecasted_period'='forecasted_period','forecast_date'='min'))
ibes_forecast_last_forecast<-inner_join(complete_ibes_data_v2,largest_forecast_date_max,by=c('ticker'='ticker','forecasted_period'='forecasted_period','forecast_date'='max'))
ibes_forecast_first_forecast
ibes_forecast_last_forecast
```
# Column comparison of beat or loss
```{r}
# Using Mean Estimates for the first earnings forecast date recorded
ibes_forecast_first_forecast$above_expectations_mean<-0
ibes_forecast_first_forecast$below_expectations_mean <-0
ibes_forecast_first_forecast$above_expectations_mean[ibes_forecast_first_forecast$actual_earnings>ibes_forecast_first_forecast$meanest]<-1
ibes_forecast_first_forecast$below_expectations_mean[ibes_forecast_first_forecast$above_expectations_mean==0]<-1

# Using Median Estimates for the first earnings forecast date recorded
ibes_forecast_first_forecast$above_expectations_median<-0
ibes_forecast_first_forecast$below_expectations_median <-0
ibes_forecast_first_forecast$above_expectations_median[ibes_forecast_first_forecast$actual_earnings>ibes_forecast_first_forecast$medest]<-1
ibes_forecast_first_forecast$below_expectations_median[ibes_forecast_first_forecast$above_expectations_median==0]<-1

# Using Mean Estimates for the last earnings forecast date recorded
ibes_forecast_last_forecast$above_expectations_mean<-0
ibes_forecast_last_forecast$below_expectations_mean <-0
ibes_forecast_last_forecast$above_expectations_mean[ibes_forecast_last_forecast$actual_earnings>ibes_forecast_last_forecast$meanest]<-1
ibes_forecast_last_forecast$below_expectations_mean[ibes_forecast_last_forecast$above_expectations_mean==0]<-1

# Using Median Estimates for the last earnings forecast date recorded
ibes_forecast_last_forecast$above_expectations_median<-0
ibes_forecast_last_forecast$below_expectations_median <-0
ibes_forecast_last_forecast$above_expectations_median[ibes_forecast_last_forecast$actual_earnings>ibes_forecast_last_forecast$medest]<-1
ibes_forecast_last_forecast$below_expectations_median[ibes_forecast_last_forecast$above_expectations_median==0]<-1

ibes_forecast_first_forecast
ibes_forecast_last_forecast
```
# Now we must link back to the ticker set we are using
```{r}
ibes_forecast_first_forecast_linked<-inner_join(ibes_forecast_first_forecast,link_tool_ticker, by = c('ticker'='TICKER'))
ibes_forecast_last_forecast_linked<-inner_join(ibes_forecast_last_forecast,link_tool_ticker, by = c('ticker'='TICKER'))
ibes_forecast_first_forecast_linked
ibes_forecast_last_forecast_linked
```
# Save these IBES forecasts 
```{r}
write.csv(ibes_forecast_first_forecast_linked,"ibes_forecast_first_forecast_linked.csv")
write.csv(ibes_forecast_last_forecast_linked,"ibes_forecast_last_forecast_linked.csv")
```
##################################################################################################################################################################################################################################
CRSP data
##################################################################################################################################################################################################################################
```{r}
# hexcd 1 = NYSE, hexcd 2 = AMEX, hexcd 3 = NASDAQ 
res <- dbSendQuery(wrds, "select date,permno,cusip,prc, ret, vol, shrout ,hexcd, cfacpr from crspa.msf
                   where prc >0")
crsp_data <- dbFetch(res, n=-1)
dbClearResult(res)
```
# Adjust the price and omit nas
```{r}
col_order <- c("date","year", "month", "permno","cusip", "price","monthly_returns","volume","shares_outstanding","market_capitalization","exchange")
# Omit all rows with incomplete data
crsp_data_v1<-crsp_data%>%drop_na(cfacpr,vol,prc,shrout,ret)
# Adjust Price by price adjustment factor 
crsp_data_v1$prc <- abs(crsp_data_v1$prc)/crsp_data_v1$cfacpr
head(crsp_data_v1)
```
# Match this to crsp link
```{r}
crsp_data_v2<- inner_join(crsp_data_v1, link_tool_ticker,by=c('permno'='PERMNO'))
head(crsp_data_v2)
```
# Get price as of the last day of april 
```{r}
crsp_data_v3<-crsp_data_v2
crsp_data_v3$price_month <- format(crsp_data_v3$date,"%m")
crsp_data_v3<-crsp_data_v3%>%filter(price_month=='04')
head(crsp_data_v3)
```
# Screen to only get one entry per permno per date 
```{r}
crsp_data_v4<-crsp_data_v3
crsp_data_v4<-crsp_data_v4%>%distinct(permno,date,.keep_all = TRUE)
crsp_data_v4<-crsp_data_v4%>%group_by(permno)
crsp_data_v4
```
# save this csv
```{r}
write.csv(crsp_data_v4, "crsp_data_vf.csv")
```
##################################################################################################################################################################################################################################
Now we want to merge the three databases to form our quartiles
##################################################################################################################################################################################################################################
```{r}
compustat_data<-read.csv("compustat_data_vf.csv",header = TRUE)
crsp_data<-read.csv("crsp_data_vf.csv",header = TRUE)
IBES_data<-read.csv("ibes_forecast_last_forecast_linked.csv", header=TRUE)
compustat_data<-compustat_data%>%group_by(gvkey)
crsp_data<-crsp_data%>%group_by(permno)
IBES_data<-IBES_data%>%group_by(ticker)
compustat_data
crsp_data
IBES_data
```
# Get only the columns we want from each table 
```{r}
# Take the columsn we need
columns<-c('fyear','ibtic','NCUSIP','PERMNO','bkvlps','epsfx')
modified_compustat_data<-compustat_data[,columns]
columns<-c('date','permno','prc','TICKER')
modified_crsp_data<-crsp_data[,columns]
columns<-c('ticker','PERMNO','cname','forecast_date','actual_earnings','forecasted_period','above_expectations_mean','above_expectations_median','below_expectations_mean','below_expectations_median','numest')
modified_ibes_data<-IBES_data[,columns]
modified_compustat_data
modified_crsp_data
modified_ibes_data
```
# Get the fiscl year prior 
```{r}
modified_crsp_data$date<-as.Date(modified_crsp_data$date)
modified_crsp_data$year<- format(modified_crsp_data$date,"%Y")
modified_crsp_data$year<-as.numeric(modified_crsp_data$year)
modified_crsp_data$previous_year<-modified_crsp_data$year-1
columns<-c('permno','TICKER','date','prc', 'previous_year')
modified_crsp_data<-modified_crsp_data[,columns]
modified_crsp_data
```
# Merge Crsp and Compustat
```{r}
merged_crsp_compustat<-inner_join(modified_compustat_data,modified_crsp_data,by=c('PERMNO'='permno', 'ibtic'='TICKER','fyear'='previous_year'))
merged_crsp_compustat<-merged_crsp_compustat%>%drop_na(epsfx)
merged_crsp_compustat$PE_Ratio<-merged_crsp_compustat$prc/merged_crsp_compustat$epsfx
merged_crsp_compustat$PB_Ratio<-merged_crsp_compustat$prc/merged_crsp_compustat$bkvlps
merged_crsp_compustat
```
# Quartile the data on PB and PE
```{r}
merged_crsp_compustat<-merged_crsp_compustat%>%group_by(fyear)%>%mutate(quartile_PE_ratio=ntile(PE_Ratio,4))
merged_crsp_compustat<-merged_crsp_compustat%>%group_by(fyear)%>%mutate(quartile_PB_ratio=ntile(PB_Ratio,4))
# Take only the top and bottom quartiles
merged_crsp_compustat<-merged_crsp_compustat%>%filter(quartile_PE_ratio==4|quartile_PE_ratio==1|quartile_PB_ratio==4|quartile_PB_ratio==1)
# Set up dummies if Price to book value 
merged_crsp_compustat$value_stock_PB<-0
merged_crsp_compustat$value_stock_PB[merged_crsp_compustat$quartile_PB_ratio==1]<-1
# Set up dummies if Price to Earnings value 
merged_crsp_compustat$value_stock_PE<-0
merged_crsp_compustat$value_stock_PE[merged_crsp_compustat$quartile_PE_ratio==1]<-1
# Set up dummies if Price to book value 
merged_crsp_compustat$growth_stock_PB<-1
merged_crsp_compustat$growth_stock_PB[merged_crsp_compustat$value_stock_PB==1]<-0
# Set up dummies if Price to book value 
merged_crsp_compustat$growth_stock_PE<-1
merged_crsp_compustat$growth_stock_PE[merged_crsp_compustat$value_stock_PE==1]<-0
merged_crsp_compustat
```
# Take the columns we need to prep for merge to ibes
```{r}
# Get the columns we need
columns<-c('ibtic','PERMNO','fyear','date','value_stock_PB','value_stock_PE','growth_stock_PB','growth_stock_PE')
merged_crsp_compustat_modified<-merged_crsp_compustat[,columns]
merged_crsp_compustat_modified
# Prep IBES to get out fiscal year prediction
modified_ibes_data$forecasted_period<-as.Date(modified_ibes_data$forecasted_period)
modified_ibes_data$year<- format(modified_ibes_data$forecasted_period,"%Y")
columns<-c('ticker','PERMNO','year','cname','above_expectations_mean','above_expectations_median','below_expectations_mean','below_expectations_median','numest')
modified_ibes_data<-modified_ibes_data[,columns]
modified_ibes_data
```
# Merge to ibes
```{r}
# Covert char to numeric
modified_ibes_data$year<-as.numeric(modified_ibes_data$year)
consolidated_crsp_compustat_ibes<-inner_join(merged_crsp_compustat_modified,modified_ibes_data, by = c('fyear'='year','ibtic'='ticker','PERMNO'='PERMNO'))
consolidated_crsp_compustat_ibes<-consolidated_crsp_compustat_ibes%>%distinct(ibtic,PERMNO,fyear,date,.keep_all=TRUE)
consolidated_crsp_compustat_ibes
```
# Organize and clean the database
```{r}
columns<-c('ibtic','PERMNO','cname','fyear','date','value_stock_PB','value_stock_PE','growth_stock_PB','growth_stock_PE','above_expectations_median','below_expectations_mean','below_expectations_median')
consolidated_crsp_compustat_ibes_vf<-consolidated_crsp_compustat_ibes
consolidated_crsp_compustat_ibes_vf<-consolidated_crsp_compustat_ibes_vf[,columns]
consolidated_crsp_compustat_ibes_vf<-rename(consolidated_crsp_compustat_ibes_vf,IBES_Ticker_ID=ibtic, CRSP_Permno_ID=PERMNO,Fiscal_Year=fyear,Stock_Price_Date=date,Company_Name=cname)
consolidated_crsp_compustat_ibes_vf
```
# Save the consolidate data
```{r}
write.csv(consolidated_crsp_compustat_ibes_vf,"consolidated_crsp_compustat_ibes_vf.csv")
```
##################################################################################################################################################################################################################################
Now we want to get 90 day return and then one year return on the stock 
##################################################################################################################################################################################################################################
```{r}
columns<-c('IBES_Ticker_ID','CRSP_Permno_ID','Company_Name','Fiscal_Year','Stock_Price_Date')
forward_dates<-consolidated_crsp_compustat_ibes_vf[,columns]
forward_dates$date_add_90<-forward_dates$Stock_Price_Date+90
forward_dates$date_add_one_year<-forward_dates$Stock_Price_Date+365
forward_dates$quarter_month<-format(forward_dates$date_add_90,"%m")
forward_dates$quarter_year<-format(forward_dates$date_add_90,"%Y")
forward_dates$future_month<-format(forward_dates$date_add_one_year,"%m")
forward_dates$future_year<-format(forward_dates$date_add_one_year,"%Y")
forward_dates
```
#Get the crsp price data again 
```{r}
# hexcd 1 = NYSE, hexcd 2 = AMEX, hexcd 3 = NASDAQ 
res <- dbSendQuery(wrds, "select date,permno,prc, cfacpr from crspa.msf
                   where prc >0")
crsp_price_data <- dbFetch(res, n=-1)
dbClearResult(res)
head(crsp_price_data)
```
# Now we only wnat to keep price that are relevant 
```{r}
crsp_price_data_v1<-crsp_price_data
crsp_price_data_v1<-crsp_price_data_v1%>%group_by(permno)
crsp_price_data_v1<-crsp_price_data_v1%>%drop_na(prc)
# Modify the price
crsp_price_data_v1$prc <- abs(crsp_price_data_v1$prc)/crsp_price_data_v1$cfacpr
# Break out the date 
crsp_price_data_v1$month<-format(crsp_price_data_v1$date,"%m")
crsp_price_data_v1$year<-format(crsp_price_data_v1$date,"%Y")
crsp_price_data_v1
```
# Clean up both sets
```{r}
# Clean up pulled crsp data
columns<-c('date','permno','prc','month','year')
crsp_price_data_v2<-crsp_price_data_v1[,columns]
# Partition forward dates table
columns<-c('CRSP_Permno_ID','Stock_Price_Date','quarter_month','quarter_year','future_month','future_year')
forward_dates_v2<-forward_dates[,columns]
crsp_price_data_v2
forward_dates_v2
```
# Join to get full data 
```{r}
original_security_price<-inner_join(forward_dates_v2,crsp_price_data_v2,by=c('CRSP_Permno_ID'='permno','Stock_Price_Date'='date'))
columns<-c('CRSP_Permno_ID','Stock_Price_Date','prc')
original_security_price<-original_security_price[,columns]

future_quarter_security_price<-inner_join(forward_dates_v2,crsp_price_data_v2,by=c('CRSP_Permno_ID'='permno','quarter_month'='month','quarter_year'='year'))
columns<-c('CRSP_Permno_ID','Stock_Price_Date','prc')
future_quarter_security_price<-future_quarter_security_price[,columns]
future_quarter_security_price<-rename(future_quarter_security_price,quarter_after_price=prc)

future_year_security_price<-inner_join(forward_dates_v2,crsp_price_data_v2,by=c('CRSP_Permno_ID'='permno','future_month'='month','future_year'='year'))
columns<-c('CRSP_Permno_ID','Stock_Price_Date','prc')
future_year_security_price<-future_year_security_price[,columns]
future_year_security_price<-rename(future_year_security_price,year_after_price=prc)

original_security_price
future_quarter_security_price
future_year_security_price
```
# Join to get all of these price data together
```{r}
consolidated_pricing_data<-inner_join(original_security_price, future_quarter_security_price,by=c('CRSP_Permno_ID'='CRSP_Permno_ID','Stock_Price_Date'='Stock_Price_Date'))
consolidated_pricing_data<-inner_join(consolidated_pricing_data, future_year_security_price,by=c('CRSP_Permno_ID'='CRSP_Permno_ID','Stock_Price_Date'='Stock_Price_Date'))
consolidated_pricing_data$quarter_after_return<-consolidated_pricing_data$quarter_after_price/consolidated_pricing_data$prc-1
consolidated_pricing_data$annual_after_return<-consolidated_pricing_data$year_after_price/consolidated_pricing_data$prc-1
columns<-c("CRSP_Permno_ID","Stock_Price_Date",'quarter_after_return','annual_after_return')
consolidated_pricing_data<-consolidated_pricing_data[,columns]
consolidated_pricing_data
```
# Save this CSV
```{r}
write.csv(consolidated_pricing_data,"consolidated_pricing_data.csv")
```
##################################################################################################################################################################################################################################
Merge Pricing back to our original csv 
##################################################################################################################################################################################################################################
```{r}
consolidated_crsp_compustat_ibes_vf
consolidated_pricing_data
consolidated_data_vf<-inner_join(consolidated_crsp_compustat_ibes_vf,consolidated_pricing_data,by=c('CRSP_Permno_ID'='CRSP_Permno_ID','Stock_Price_Date'='Stock_Price_Date'))
consolidated_data_vf
```
# Write this into csv format
```{r}
write.csv(consolidated_data_vf,"consolidated_data_vf.csv")
```
##################################################################################################################################################################################################################################
Look at YOY Returns 
##################################################################################################################################################################################################################################
```{r}
consolidated_data_vf<-consolidated_data_vf%>%drop_na(quarter_after_return, annual_after_return)
consolidated_data_vfs
```
# Group by year and value and above by median
```{r}
# Using Price to Book
value_by_price_to_book_perform_above<-consolidated_data_vf%>%filter(value_stock_PB==1 & above_expectations_median==1)
value_by_price_to_book_perform_below<-consolidated_data_vf%>%filter(value_stock_PB==1 & above_expectations_median==0)
growth_by_price_to_book_perform_above<-consolidated_data_vf%>%filter(growth_stock_PB==1& above_expectations_median==1)
growth_by_price_to_book_perform_below<-consolidated_data_vf%>%filter(growth_stock_PB==1 & above_expectations_median==0)

# Using Price to Earnings
value_by_price_to_earnings_perform_above<-consolidated_data_vf%>%filter(value_stock_PE==1 & above_expectations_median==1)
value_by_price_to_earnings_perform_below<-consolidated_data_vf%>%filter(value_stock_PE==1 & above_expectations_median==0)
growth_by_price_to_earnings_perform_above<-consolidated_data_vf%>%filter(growth_stock_PE==1 & above_expectations_median==1)
growth_by_price_to_earnings_perform_below<-consolidated_data_vf%>%filter(growth_stock_PE==1 & above_expectations_median==0)

#Get the average return per year above, PB value
value_by_price_to_book_perform_above$average_quaterly_return<-mean(value_by_price_to_book_perform_above$quarter_after_return)
value_by_price_to_book_perform_above$average_annual_return<-mean(value_by_price_to_book_perform_above$annual_after_return)

#Get the average return per year below, PB value
value_by_price_to_book_perform_below$average_quaterly_return<-mean(value_by_price_to_book_perform_below$quarter_after_return)
value_by_price_to_book_perform_below$average_annual_return<-mean(value_by_price_to_book_perform_below$annual_after_return)


#Get the average return per year above, PB Growth
growth_by_price_to_book_perform_above$average_quaterly_return<-mean(growth_by_price_to_book_perform_above$quarter_after_return)
growth_by_price_to_book_perform_above$average_annual_return<-mean(growth_by_price_to_book_perform_above$annual_after_return)

#Get the average return per year below, PB Growth
growth_by_price_to_book_perform_below$average_quaterly_return<-mean(growth_by_price_to_book_perform_below$quarter_after_return)
growth_by_price_to_book_perform_below$average_annual_return<-mean(growth_by_price_to_book_perform_below$annual_after_return)

#Get the average return per year above, PE value
value_by_price_to_earnings_perform_above$average_quaterly_return<-mean(value_by_price_to_earnings_perform_above$quarter_after_return)
value_by_price_to_earnings_perform_above$average_annual_return<-mean(value_by_price_to_earnings_perform_above$annual_after_return)

#Get the average return per year below, PB value
value_by_price_to_earnings_perform_below$average_quaterly_return<-mean(value_by_price_to_earnings_perform_below$quarter_after_return)
value_by_price_to_earnings_perform_below$average_annual_return<-mean(value_by_price_to_earnings_perform_below$annual_after_return)

#Get the average return per year above, PB Growth
growth_by_price_to_earnings_perform_above$average_quaterly_return<-mean(growth_by_price_to_earnings_perform_above$quarter_after_return)
growth_by_price_to_earnings_perform_above$average_annual_return<-mean(growth_by_price_to_earnings_perform_above$annual_after_return)

#Get the average return per year below, PB Growth
growth_by_price_to_earnings_perform_below$average_quaterly_return<-mean(growth_by_price_to_earnings_perform_below$quarter_after_return)
growth_by_price_to_earnings_perform_below$average_annual_return<-mean(growth_by_price_to_earnings_perform_below$annual_after_return)

#Output Results P/B
value_by_price_to_book_perform_above
value_by_price_to_book_perform_below
growth_by_price_to_book_perform_above
growth_by_price_to_book_perform_below

#Output Results P/E
value_by_price_to_earnings_perform_above
value_by_price_to_earnings_perform_below
growth_by_price_to_earnings_perform_above
growth_by_price_to_earnings_perform_below
```
# Concat this to get just one value 
```{r}
value_by_price_to_book_perform_above_summary<-value_by_price_to_book_perform_above%>%distinct(Fiscal_Year,.keep_all = TRUE)
value_by_price_to_book_perform_below_summary<-value_by_price_to_book_perform_below%>%distinct(Fiscal_Year,.keep_all = TRUE)
growth_by_price_to_book_perform_above_summary<-growth_by_price_to_book_perform_above%>%distinct(Fiscal_Year,.keep_all = TRUE)
growth_by_price_to_book_perform_below_summary<-growth_by_price_to_book_perform_below%>%distinct(Fiscal_Year,.keep_all = TRUE)

value_by_price_to_book_perform_above_summary<-arrange(value_by_price_to_book_perform_above_summary,Fiscal_Year)
value_by_price_to_book_perform_below_summary<-arrange(value_by_price_to_book_perform_below_summary,Fiscal_Year)
growth_by_price_to_book_perform_above_summary<-arrange(growth_by_price_to_book_perform_above_summary,Fiscal_Year)
growth_by_price_to_book_perform_below_summary<-arrange(growth_by_price_to_book_perform_below_summary,Fiscal_Year)

aggregate_price_to_book<-rbind(value_by_price_to_book_perform_above_summary,value_by_price_to_book_perform_below_summary,growth_by_price_to_book_perform_above_summary,growth_by_price_to_book_perform_below_summary)
aggregate_price_to_book<-aggregate_price_to_book%>%group_by(Fiscal_Year)
aggregate_price_to_book<-arrange(aggregate_price_to_book,Fiscal_Year)

value_by_price_to_book_perform_above_summary

```
# Concat this to get just one value 
```{r}
value_by_price_to_earnings_perform_above_summary<-value_by_price_to_earnings_perform_above%>%distinct(Fiscal_Year,.keep_all = TRUE)
value_by_price_to_earnings_perform_below_summary<-value_by_price_to_earnings_perform_below%>%distinct(Fiscal_Year,.keep_all = TRUE)
growth_by_price_to_earnings_perform_above_summary<-growth_by_price_to_earnings_perform_above%>%distinct(Fiscal_Year,.keep_all = TRUE)
growth_by_price_to_earnings_perform_below_summary<-growth_by_price_to_earnings_perform_below%>%distinct(Fiscal_Year,.keep_all = TRUE)

value_by_price_to_earnings_perform_above_summary<-arrange(value_by_price_to_earnings_perform_above_summary,Fiscal_Year)
value_by_price_to_earnings_perform_below_summary<-arrange(value_by_price_to_earnings_perform_below_summary,Fiscal_Year)
growth_by_price_to_earnings_perform_above_summary<-arrange(growth_by_price_to_earnings_perform_above_summary,Fiscal_Year)
growth_by_price_to_earnings_perform_below_summary<-arrange(growth_by_price_to_earnings_perform_below_summary,Fiscal_Year)

aggregate_price_to_earnings<-rbind(value_by_price_to_earnings_perform_above_summary,value_by_price_to_earnings_perform_below_summary,growth_by_price_to_earnings_perform_above_summary,growth_by_price_to_earnings_perform_below_summary)
aggregate_price_to_earnings<-aggregate_price_to_earnings%>%group_by(Fiscal_Year)
aggregate_price_to_earnings<-arrange(aggregate_price_to_earnings,Fiscal_Year)
aggregate_price_to_earnings
```
# Make a for aggregate returns given price to earnings
```{r}
aggregate_price_to_earnings$type_of_security_PB<-"NA"
aggregate_price_to_earnings$type_of_security_PB[aggregate_price_to_earnings$value_stock_PB==1&aggregate_price_to_earnings$above_expectations_median==1]<-"Value Stock Above Expectations"
aggregate_price_to_earnings$type_of_security_PB[aggregate_price_to_earnings$value_stock_PB==1&aggregate_price_to_earnings$above_expectations_median==0]<-"Value Stock Below Expectations"
aggregate_price_to_earnings$type_of_security_PB[aggregate_price_to_earnings$growth_stock_PB==1&aggregate_price_to_earnings$above_expectations_median==1]<-"Growth Stock Above Expectations"
aggregate_price_to_earnings$type_of_security_PB[aggregate_price_to_earnings$growth_stock_PB==1&aggregate_price_to_earnings$above_expectations_median==0]<-"Growth Stock Below Expectations"

aggregate_price_to_earnings$type_of_security_PE<-"NA"
aggregate_price_to_earnings$type_of_security_PE[aggregate_price_to_earnings$value_stock_PE==1&aggregate_price_to_earnings$above_expectations_median==1]<-"Value Stock Above Expectations"
aggregate_price_to_earnings$type_of_security_PE[aggregate_price_to_earnings$growth_stock_PE==1&aggregate_price_to_earnings$above_expectations_median==1]<-"Growth Stock Above Expectations"
aggregate_price_to_earnings$type_of_security_PE[aggregate_price_to_earnings$value_stock_PE==1&aggregate_price_to_earnings$above_expectations_median==0]<-"Value Stock Below Expectations"
aggregate_price_to_earnings$type_of_security_PE[aggregate_price_to_earnings$growth_stock_PE==1&aggregate_price_to_earnings$above_expectations_median==0]<-"Growth Stock Below Expectations"
```
# Mutate the data so we can work with it 
```{r}
columns<-c('Fiscal_Year','quarter_after_return','annual_after_return','type_of_security_PB','type_of_security_PE')
aggregate_price_to_earnings_v1<-aggregate_price_to_earnings[,columns]
aggregate_price_to_earnings_v1
```
#Write into Excel
```{r}
write.csv(value_by_price_to_book_perform_above_summary,"value_by_price_to_book_perform_above_summary.csv")
write.csv(value_by_price_to_book_perform_below_summary,"value_by_price_to_book_perform_below_summary.csv")
write.csv(growth_by_price_to_book_perform_above_summary,"growth_by_price_to_book_perform_above_summary.csv")
write.csv(growth_by_price_to_book_perform_below_summary,"growth_by_price_to_book_perform_below_summary.csv")

write.csv(value_by_price_to_earnings_perform_above_summary,"value_by_price_to_earnings_perform_above_summary.csv")
write.csv(value_by_price_to_earnings_perform_below_summary,"value_by_price_to_earnings_perform_below_summary.csv")
write.csv(growth_by_price_to_earnings_perform_above_summary,"growth_by_price_to_earnings_perform_above_summary.csv")
write.csv(growth_by_price_to_earnings_perform_below_summary,"growth_by_price_to_earnings_perform_below_summary.csv")

```

